---
title: "Bank of Israel data import functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{boi_functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, echo = FALSE, message = FALSE, warning = FALSE,
  comment = "#>"
)
```

```{r setup}
library(MiscImport)
```

The `import_boi_*` family of functions is designed to download data from
Bank of Israel website. The data is divided by topics.

# Institutional investors

Institutional investors consist of the following types:

* Pension funds
* Providence (gemel and hishtalmut) funds 
* Insurance companies

## Summary data

The summary data section presents summary data (on all investor types) 
according to the following segmentaion:

* Tradability - monthly data that distinguishes between traded and non traded
assets.

* Distribution of local currency (ILS) assets of institutional investors

* The total (domestic and foreign) asset class distribution of the portfolio
of institutional investors

* Linkage - monthly data that distinguishes between various (CPI or FX) 
linkages.



```{r}

```

